\section{\label{sec:analysis.simulation}Monte-Carlo}
There are certain kinematic regions of \abbr{CLAS} in which physics events are not being recorded properly i.e.~the area dividing each sector in \abbr{CLAS}. Furthermore each sector in \abbr{CLAS} is asymmetric in the acceptance of events due to subsystem inefficiencies such as inoperable \abbr{DC} wires, \abbr{PMT} inefficiencies, dead scintillator strips the the \abbr{TOF} and \abbr{ST} subsystems. When a triggered event is recorded and reconstructed these asymmetric inefficiencies factors are reflected and must be carefully understood because these factors are properties of the \abbr{CLAS} detector and independent of any physics that occurred. To properly understand the detector effects on the data, \abbr{CLAS} utilizes a \abbr{GEANT} simulation package know as \abbr{GSIM}. To prepare an event for \abbr{GSIM} the program \abbr{GAMP2PART} converts a text file, containing the 4-momentum of the generated event, into a suitable file format for \abbr{GSIM}. \abbr{GSIM} then simulates the passage of these particles through the \abbr{CLAS} detector and generates the associated \abbr{ADC} and \abbr{TDC} information from detector hits. \abbr{GSIM} takes into account detector inefficiencies described in the \abbr{\texttt{CLAS\_CALDB\_RUNINDEX}}. The \abbr{CLAS\_CALDB\_RUNINDEX} is an array of information about each subsystem's inefficiency that was derived during the \g12 calibration process. The \abbr{GSIM} simulated hits are then ``post-processed'' by smearing the \abbr{TDC} and \abbr{ADC} hits to imitate the observed resolution of the detector subsystems using the program \abbr{GPP} (\abbr{GSIM} post-processor). \abbr{GPP} also removes detector hits due to inefficient \abbr{DC} wires.

 The acceptance for the cross-sections presented in this work was measured using phase-space Monte-Carlo (\abbr{MC}\label{abbr:mc}) simulation, using PLUTO++~\cite{PLUTO} as the generator, for the reaction channels,
\begin{subequations}
	\begin{align}
			\gamma \p \rightarrow & \ p \pi^{0} \nonumber \\[-0.4em]
			& \ \hookrightarrow p \gamma \gamma \nonumber \\[-0.4em]
			& \qquad \hookrightarrow p e^+ e^- \gamma
			\label{eq:simproduct1}
		\end{align}
		\begin{align}
			\gamma \p \rightarrow & \ p \pi^{0} \nonumber \\[-0.4em]
			& \ \hookrightarrow p e^+ e^- \gamma.
			\label{eq:simproduct2}
		\end{align}
	\end{subequations} 
	A total of events, $N_g$, was generated and this number was weighted by the relative branching ratios found in Table~\ref{tab:targetspecs} to resemble the conditions of the data. The number of events generated for the reaction channel~\ref{eq:simproduct1} can be found in Table~\ref{tab:simnumspecs} as $N_c$. The number of events generated for the reaction channel n~\ref{eq:simproduct2} can be found in Table~\ref{tab:simnumspecs} as $N_d$.
	\input{tables/simnumspecs.tex}
	After the events are generated, they are inputted into the \abbr{CLAS} simulation chain \abbr{GAMP2BOS}\label{abbr:gamp2bos}, \abbr{GSIM}\label{abbr:gsim}, \abbr{GPP}\label{abbr:gpp}, and then reconstructed with the same program used to reconstruct the data, \abbrlc{}{a1c}\label{abbr:a1c}, all programs in the simulation chain use the parameters and the run index described above. Once the events are processed through \abbrlc{}{a1c}, the cuts described in Secs.~\ref{sec:analysis.data.reduction}, ~\ref{sec:analysis.fitting.compare}, are applied as they are to the real data. The acceptance $\eta(E_\gamma,\theta^{\pi^0}_{C.M.})$ is then determined by adding the simulations for the conversion and the dalitz, then for photon energy bins of 25 MeV increments and $\Delta\cos\theta^{\pi^0}_{C.M.} = 0.0125$ increments, the ratio of reconstructed events ($N_R$) to generated events ($N_G$) yields,
	\begin{equation}\label{eq:acceptance}
	\eta(E_\gamma,\cos\theta^{\pi^0}_{C.M.}) = \frac{N_R(E_\gamma,\cos\theta^{\pi^0}_{C.M.})}{N_G(E_\gamma,\cos\theta^{\pi^0}_{C.M.})} \ .
	\end{equation}
	The $\Delta\cos\theta^{\pi^0}_{C.M.}$ binning in the acceptance is a factor of 2.4 finer than the smallest $\Delta\cos\theta^{\pi^0}_{C.M.}$ increment used in the cross-section measurement. If an accurate physics model for the generator had been used, as was in Sec.~\ref{sec:analysis.simulation}, the binning for the acceptance  would not have had to be so fine.


\subsection{Simulating the Lepton Trigger}\label{sec:analysis.accept.trigger}
During the collection process, for an event to be written by the \abbr{DAQ} it must have passed at least one of the trigger ``bits" defined in Sec.~\ref{sec:clas.g12.conditions.data}. As discussed in Sec.~\ref{sec.data.trig.lepton}, the process of lepton triggering required a coincidence between the \abbr{EC} and the \abbr{CC} subsystems. This coincidence was established by using the voltage sum of the \abbr{CC} for a sector and the voltage sum of the \abbr{EC} for the same sector and comparing each sum to a preset threshold described in Table~\ref{tab:data.ecccthresh}. However when \abbr{GSIM} simulates tracks through the \abbr{CC} and \abbr{EC}, it does not account for the minimum voltage threshold that was required for data collection, moreover the simulation of the trigger must match the trigger efficiency discussed in Sec.~\ref{sec:analysis.trigger.verify}.

Simulation of the \abbr{CC} and \abbr{EC} trigger ``bit 6'', Sec.~\ref{sec.data.trig.lepton}, was performed by writing an algorithm that attempted to mimic the method in which triggered data was recorded. To accomplish this a modified function, written by Simeon McAleer from FSU, was written into the simulation reconstruction algorithm. The routine returned the sector and a boolean of 0 or 1 (pass or fail), that simulated the trigger based on the following criteria;
\begin{enumerate}\label{trig:sim.all}
	\item The sector with the highest EC summed energy over threshold. \label{trig:sim.ECtot} 
	\item The sector with the highest EC Inner Layer summed energy over threshold. \label{trig:sim.ECinner} 
	\item The sector with the highest CC summed energy over threshold. \label{trig:sim.CCtot} 
	\item All three above conditions must be in same sector.
\end{enumerate}
Thresholds as described in Table~\ref{tab:data.ecccthresh} are 80~mV, 60~mV and 20~mV for \abbr{EC} \emph{inner}, \abbr{EC}\emph{total} and CC respectively. The \abbr{CC} trigger threshold was applied to groups of eight \abbr{CC} \abbr{PMT}s, called ``sim bits''. The ``sim bits'' were staggered by four \abbr{PMT}s so that each \abbr{PMT} goes into two ``sim bits'', after which all ``sim bits'' were ``\emph{OR}'''d together. If any ``sim bit'' calculated as above threshold, that specific sector was then compared to the remaining sectors to establish the condition listed in~\ref{trig:sim.CCtot}.

The \abbr{EC} \emph{inner} and \abbr{EC} \emph{total} trigger thresholds were applied to all \abbr{EC} strips in a sector. This was done by summing over the energy for every strip in every orientation of the \abbr{EC} per sector. If the energy summation for the \abbr{EC} \emph{inner} was above threshold,   that specific sector was then compared to the remaining sectors to establish the condition listed in~\ref{trig:sim.ECinner}. If the energy summation for the \abbr{EC} \emph{total} was above threshold, that specific sector was then compared to the remaining sectors to establish the condition of the sector with the highest EC summed energy over threshold.

\subsubsection{Validity of Trigger Simulation}
The actual triggered data could have been triggered by the following sceneries;
\begin{enumerate}\label{trig:get.all}
	\item $e^-$ \abbr{CC} and \abbr{EC} hit above preset thresholds,
	\item $e^+$ \abbr{CC} and \abbr{EC} hit above preset thresholds,
	\item $e^-$ \abbr{CC} hit above preset thresholds and $e^+$ \abbr{EC} hit above preset thresholds in the same sector, 
	\item $e^-$ \abbr{EC} hit above preset thresholds and $e^+$ \abbr{CC} hit above preset thresholds in the same sector. 
\end{enumerate}
The lepton trigger ``bit 6" was 100\% efficient (see Sec.~\ref{sec:analysis.trigger.verify}) when the data was cut using all the conditions listed above (1, 2, 3, 4) using an ``OR" flag. This means that a $\gamma p \to p e^+ e^-$ event must satisfy at least one of the listed conditions. The reduction in events when at least one of the conditions was satisfied was 69.91\%. Prior to simulating the trigger, cutting the \abbr{MC} with the listed conditions reduced the event yield by 81.91\%. Simulating the trigger and cutting on the \abbr{MC} events with the listed conditions reduced that event yield to 69.48\%. This indicates that the trigger simulation is properly mimicking the trigger configuration used when data is collected. 

\section{PLUTO++ Event Generator}\label{sec:pluto}

Pluto~\cite{PLUTO} is a Monte-Carlo event generator designed for the study of hadronic interactions and heavy ion reactions in \abbr{HADES}, \abbr{FAIR} and upcoming \abbr{PANDA} collaborations. The versatility of Pluto enables its use as an event generator for photoproduction in \abbr{CLAS}. For hadronic interactions, Pluto can generate interactions from pion production threshold to intermediate energies of a few~GeV per nucleon. The entire software package is based on ROOT and uses ROOT's embedded C++ interpreter to control the generation of events. Programming event reaction can be set up with a few lines of ROOT macro code without detailed knowledge of programming. Some features in Pluto are, but not limited to;
\begin{itemize}
	\item Ability to generate events in phase space.
	\item Ability to generate events with a continuous bremsstrahlung photon beam.
	\item Ability to generate events weighted by a user defined $t$-slope.
	\item Ability to generate events weighted by a user defined cross-section.
	\begin{itemize}
		\item Total cross section can be inputted via functional form or histogram.
		\item Differential cross sections can be inputted via functional forms or histograms for specific beam energies up to 110 histograms relating to intervals of beam energy.
	\end{itemize}
	\item Ability to generate events that decay via already established physics parameters, i.e.~transition form factors.
	\item Ability to generate events that decay via modified established physics parameters.
	\item Ability to generate events with multiple production channels, weighted by user inputted cross-section probability.
	\item Ability to generate events with multiple decay channels, weighted by user inputted branching ratio.
	\item Ability to perform vertex smearing.
	\item Ability to create virtual detectors.
\end{itemize}

For the analysis presented in this work, Pluto was used in conjunction with known differential cross sections to verify simulation momentum smearing and tagger resolution, Sec.~\ref{sec:analysis.simsmear.verify}. Pluto was also utilized as a phase space generator in this analysis, to perform a ``tune'' on the kinematic fitter, Sec.~\ref{sec:analysis.fitting}, to calculate the acceptance corrections Sec.~\ref{sec:results.acceptance}, and to calculate the normalization Sec.~\ref{sec:results.normalization}.