\section{Experimental Setup}\label{sec:setup}
	The measurements used for this analysis was taken with the \abbr{CLAS} detector at Hall B at the Thomas Jefferson National Accelerator Facility \abbr{TJNAF} located in 
	Newport News, Virginia. The \g12 experiment is a photoproduction experiment, it ran during March - June 2008 with a total of 44 days of good beam time. It collected over 
	128~TB of raw data that consisted of $26\cdot 10^9$ events, with an integrated luminosity of 68~pb$^{-1}$. The photon beam was produced by impinging a $5.715$~GeV 
	electron beam, at 65nA, on a Au radiator of $10^{-4}$ radiation length. Photons in the energy range from 20\% to 95\% of the electron beam
	energy were tagged, resulting in a photon beam energy range of 1.1-5.5~GeV. This photon beam was then collimated before being introduced onto a $\ell H_2$ target 40~cm in 
	length along the z-direction and 2~cm radius. The placement of the target was 90~cm upstream from \abbr{CLAS} center (toward Au radiator), this increased the acceptance 
	of particles in the forward direction. During the runtime of \g12, the Cherenkov detectors were filled with perfluorobutane ($\mathrm{C_4F_{10}}$) allowing for electron/positron 
	detection. The experiment had a dedicated trigger, amongst 9 other triggers, that consisted of Cherenkov Counter(\abbr{CC}) and Electro-magnetic Calorimeter(\abbr{EC}) 
	coincidence hits for the entire beam energy range. With proper cuts on the \abbr{CC} and \abbr{EC} a $\pi/e$ rejection of $10^6$ for $e^{\pm}$ pairs was established.